\section{Feature Summary}
DART offers many useful features to aid the process of robotic controller design. In this document highlights a set of important features based on DART 5.0.

\paragraph{General}
\begin{itemize}[leftmargin=*] \itemsep1pt \parskip0pt \parsep0pt
  \item Open source under BSD licence written in C++.
  \item Support Linux, Mac OSX, and Windows.
  \item Fully integrate with Gazebo.
  \item Support models described in URDF and SDF formats.
  \item Provide default integration methods, semi-implicit Euler and RK4, as well as an extensible API for other numerical integration methods.
  \item Support multiple collision detectors: FCL, Bullet, and ODE.
  \item Support lazy evaluation and automatic update of kinematic and dynamic quantities.
  \item Provide extensible API for embedding user-provided classes into DART data structures.
  \item Support comprehensive recording of events in simulation history.
  \item Support OpenGL and OpenSceneGraph.
\end{itemize}


% - Open source written in C++
% - Supports all three operating systems
% - Fully integrate with Gazebo
% - Support URDF and SDF format
% - Support multiple collision detectors
% - Extensible numerical integration methods
% - Support lazy evaluation and automatic updating of kinematic and dynamic terms: greatly improves code safety and often improves efficiency
% - Fully extensible Addons and Nodes which allow you to embed your own classes into the kinematic and dynamic structures
% - Perfect recording of events, which includes accounting for changes to internal properties and changes to user-defined Addons and Nodes
% - Extensible GUI


\paragraph{Kinematics}
\begin{itemize}[leftmargin=*] \itemsep1pt \parskip0pt \parsep0pt
  \item Support numerous types of Joint.
  \item Support numerous primitive and arbitrary body shapes with customizable inertial and material properties.
  \item Support flexible skeleton modeling: cloning and reconfiguring skeletons or subsections of a skeleton.
  \item Provide comprehensive access to the kinematic state, such as transformations, positions, velocities, and acceleration.
  \item Provide comprehensive access to various first-order and second-order derivatives of kinematic quantities, such as Jacobian matrices and time derivative of Jacobian matrices. 
  \item Support frame semantics that enables DART structures expressed in arbitrary coordinate frames.
  \item Provide build-in IK functionalities.
\end{itemize}

% - Support numerous types of joint
% - Support arbitrary body shapes and inertial properties
% - Support flexible skeleton modeling: able to easily clone skeletons or subsections of skeletons; able to easily reconfigure the layouts of skeletons
% - API for Jacobian matrices:
% - API for the state of system: Get all kinds of positions and velocities
% - Support computation in arbitrary coordinate frames
% - Built-in IK functionality

\paragraph{Dynamics}
\begin{itemize}[leftmargin=*] \itemsep1pt \parskip0pt \parsep0pt
  \item Achieve high performance for articulated dynamic systems using Lie Group representation and Featherstone recursive algorithms.
  \item Enforce joints between body nodes exactly using generalized coordinates.
  \item Provide comprehensive API for dynamic quantities and their derivatives, such as mass matrix, Coriolis force, gravitational force, other external and internal forces.
  \item Support both rigid and soft body nodes.
  \item Model viscoelastic joint dynamics with hard joint limits.
  \item Support various types of actuators.
  \item Handle contacts and collisions using an implicit time-stepping, velocity-based LCP to guarantee non-penetration, directional friction, and approximated Coulomb friction cone conditions.
  \item Support various Cartesian constraints and provide an extensible API for user-defined constraints.
  \item Provide multiple constraint solvers: Lemke method, Dantzig method, and PSG method.
  \item Support dynamic systems with closed-loops.
\end{itemize}
% - High performance for articulated dynamic systems:Featherstone linear algorithm
% - Enforce joints exactly: Lagrangian dynamics and generalized coordinates
% - Support both rigid and soft body nodes
% - Model joint dynamics: joint limits, elasticity, damping
% - Support multiple constraint solvers
% - Support Cartesian joint constraints
% - Support closed-loop structure.
% - API for dynamic quantities: Mass matrix, Coriolis force, gravitational force, other external and internal 
% forces
% - Support numerous types of actuator



